A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-07-08 main.tex
removed an unnecessary footnote

We implement \Calculus{} for Parikh automata as described in
\cref{sec:parikh-automata}. The artefact submitted along with this paper is a
program that reads an instance file with one or more products of one or more
Parikh automaton with transition labels defined as ranges of Unicode characters,
along with a set of constraints on the final values of their registers expressed
as Presburger arithmetic in a C-like syntax. We call this program
\Catra.\footnote{If you really must read it as an acronym, please read it as
CAtegory Theory on Register Automata, or if you object to the somewhat
nonstandard use of register automata and category theory, as Check Assignments
of The Registers Afterwards. Or alternatively if you find it all to be too much
of a theoretical exercise, as Can Anyone Think of A Real Application.}

>>>>

We implement \Calculus{} for Parikh automata as described in
\cref{sec:parikh-automata}. The artefact submitted along with this paper is a
program that reads an instance file with one or more products of one or more
Parikh automaton with transition labels defined as ranges of Unicode characters,
along with a set of constraints on the final values of their registers expressed
as Presburger arithmetic in a C-like syntax. We call this program
\Catra.
% \footnote{If you really must read it as an acronym, please read it as
%CAtegory Theory on Register Automata, or if you object to the somewhat
%nonstandard use of register automata and category theory, as Check Assignments
%of The Registers Afterwards. Or alternatively if you find it all to be too much
%of a theoretical exercise, as Can Anyone Think of A Real Application.}
